Reactor like TGE model

### 2019-04-12 AYSS-2019/presentation/main.tex
ayss-2019

\begin{frame}
\frametitle{Existing model}

@@

\begin{frame}
\frametitle{Disadvantages of existing model}

\begin{frame}
    \frametitle{Reactor Like TGE model}

\begin{frame}
\frametitle{Reactor Like TGE model}

>>>>

\begin{frame}
\frametitle{Existing model}
\begin{columns}
\begin{column}{0.5\textwidth}
    \begin{figure}[htb]
        \centering
        \includegraphics[width=1\columnwidth]{01_Gurevich.pdf}
    \end{figure}
    \textbf{Gurevich model --- Runway breakdown}
\begin{itemize}
    \item Breakdown with help secondary ionization of relativistic electron
    \item If field over MIP loss - run breakdown
\end{itemize}
\end{column}
\begin{column}{0.5\textwidth}
     \textbf{Dwyer model --- Gamma and positron feedback}
    \begin{itemize}
        \item Electron emit bremsstrahlung (including directed to back)
        \item Compton scattering direct gamma to back 
        \item Gamma create new primary electron in top area of cloud
        \item Gamma ray conversion in electron-positron pair
        \item Positron accelerate by field and ionizes cloud creating new primary electron

    \end{itemize}
\end{column}
\end{columns}

@@

\begin{frame}
\frametitle{Disadvantages of existing model}
\begin{itemize}
    \item Gurevich model of runway breakdown don't give ionization for lighting initiation
    \item Dwyer model of feedback don't work in real condition [1]
    \item A long-lasting phenomena as TGE  can't exist in Dwyer model
    \item This models use uniform electric field where as field in cloud have more difficult structure 
\end{itemize}
\small{[1] Calculation of gain coefficient in Dwyer relativistic discharge feedback model of thunderstorm runway breakdown
    EPJ Web of Conferences 201, 07003 (2019), \url{https://doi.org/10.1051/epjconf/201920107003}}
\end{frame}

 % Local background must be enclosed by curly braces for grouping.
\usebackgroundtemplate{
    \hspace*{-2cm}\includegraphics[width=1.2\paperwidth]{electric_streams.pdf}

}%
\begin{frame}
    \frametitle{Reactor Like TGE model}
 \centering\includegraphics[width=0.8\paperwidth]{draw.pdf}

\end{frame}
\usebackgroundtemplate{}
\begin{frame}
\frametitle{Reactor Like TGE model}
